---
title: "R Notebook"
author: "Anusha Karunakaran"
date: "10/24/2019"
output:
  html_document:
    df_print: paged
    toc: true
    theme: united
  html_notebook: default
  pdf_document: default
name: Anusha Karunakaran
---


# Problem 1

## Problem 1.a

The expected value of X is 10.

```{r}
Expected_X <- 10
```


## Problem 1.b

The expected value of Y is 15.

```{r}
Expected_Y <- 15
```

## Problem 1.c

```{r}
Expected_Z <- 2*Expected_X + 3*Expected_Y
Expected_Z
```


## Problem 1.d

The variables Y and Z change in opposite directions.


```{r}
set.seed(100)
X <- rnorm(100,10,2)
Y <- rnorm(100,15,1)


SD_Z <- sqrt(2*2*4 + 3*3*1 + 2*2*3*cov(X,Y))
Z <- rnorm(100,Expected_Z,SD_Z)
cor(Y,Z)
```



## Problem 1.e

<b> Var(Y+Z) = Var(Y) + Var(Z) + 2*Y*Z*Cov(Y,Z) </b>

```{r}
Var_YZ <-  var(Y) +  var(Z) + 2*cov(Y,Z)
Var_YZ
``` 

## Problem 1.f

```{r}
set.seed(100)
Mean_YZ <- mean(Y) + mean(Z)
SD_YZ <- sqrt(var(Y) + var(Z) + 2*cov(Y,Z))

Simulate_YZ <- replicate(100,rnorm(1,Mean_YZ,SD_YZ))

var(Simulate_YZ)
```

# Problem 2

## Problem 2.a

<pre>
For K = 2 we have 1 – 1/K^2 = 1 - 1/4 = 3/4 = 75%. So Chebyshev’s inequality says that at least 75% of the data values of any distribution must be within two standard deviations of the mean.

For K = 3 we have 1 – 1/K^2 = 1 - 1/9 = 8/9 = 89%. So Chebyshev’s inequality says that at least 89% of the data values of any distribution must be within three standard deviations of the mean.

Maximum distribution that falls within k=2 and k=3 would be almost 1 because only a limited few values are very far off the mean, so that standard deviation is high. 

Majority of the values are very close to the mean, to increase the maximum distribution within the 2/3 standard deviations to the mean.
</pre>


## Problem 2.b

<pre>
The discrete distribution that minimizes the portion of the distribution  that falls within 2 standard deviations of the mean is 'Poission Distribution'.
The continuous distribution that minimizes the portion of the distribution  that falls within 2 standard deviations of the mean is 'Exponential Distribution'
</pre>

## Problem 2.c

<pre>
The discrete distribution that minimizes the portion of the distribution  that falls within 2 standard deviations of the mean is 'Poission Distribution'.
The continuous distribution that minimizes the portion of the distribution  that falls within 2 standard deviations of the mean is 'Exponential Distribution'
</pre>

# Problem 3

population_mean <- 120000
population_sd <- 10000


## Problem 3.a

<pre>
The sample of 10 individuals will be normally distributed.

Mean of the sample = 120,000
Standard Deviation of the sample = 10000/sqrt(10)
                                 = 3162.28
                                 
</pre>

```{r}
Sample_Size_10 <- rnorm(10,120000,10000)
mean(Sample_Size_10)
```


## Problem 3.b

```{r}
sd_3b <- 10000/sqrt(10)
Simulate_3b <- replicate(1000,rnorm(10,120000,sd_3b))
mean(Simulate_3b)
sd(Simulate_3b)
plot(Simulate_3b)
hist(Simulate_3b)
```


It is larger than the previous one.


## Problem 3.c

```{r}
sd_3c <- 10000/sqrt(10)
Simulate_3c <- replicate(10000,rnorm(10,120000,sd_3c))
mean(Simulate_3c)
sd(Simulate_3c)
plot(Simulate_3c)
hist(Simulate_3c)
```



## Problem 3.d

As we increse the replication numbers, the mean gets closer to the given mean and standard deviation decreases.

```{r}
sd_3d <- 10000/sqrt(10)
Simulate_3d <- replicate(100000,rnorm(10,120000,sd_3d))
mean(Simulate_3d)
sd(Simulate_3d)
plot(Simulate_3d)
hist(Simulate_3d)
```



## Problem 3.e

<pre>
The sample of 30 individuals will be normally distributed.The histogram for this is slightly right skewed.


Mean of the sample = 120,000
Standard Deviation of the sample = 10000/sqrt(30)
                                 = 1825.74
                                 
</pre>



```{r}
sd_3e <- 10000/sqrt(30)
Sample_Size_30 <- rnorm(30,120000,sd_3e)
mean(Sample_Size_30)
plot(Sample_Size_30)
hist(Sample_Size_30)


```




## Problem 3.f

The histogram comes out to be more normally distributed as we replicate 1000 times. Hence, more replication improves the result.

```{r}
Simulate_3f <- replicate(100000,rnorm(30,120000,10000))
mean(Simulate_3f)
sd(Simulate_3f)
plot(Simulate_3f)
hist(Simulate_3f)
```

# Problem 4

## Problem 4.a

<pre>
The multiplier for 95% confidence is 1.96
Confidence Level - 0.23 to 0.31
0.23 <- mean - 1.96*sd/sqrt(1000)
0.31 <- mean + 1.96*sd/sqrt(1000)
</pre>

```{r}
n <- 1000
mean <- 0.27
sd <- 0.645
sd_sample <- sd/sqrt(1000)

#P(X>0.1)
1-pnorm(0.1,mean,sd_sample)
```



## Problem 4.b

```{r}
pnorm(0.31,mean,sd_sample) -pnorm(0.23,mean,sd_sample)
```

## Problem 4.c

In any random sample atleast 10% have pet insurance. So the probability that pet owners in the sample having probability less than 0.1 is 0.


```{r}
probability <- 0.1
standard_deviation <- sqrt((probability*(1-probability))/100)
pnorm(0.05,probability,standard_deviation) -pnorm(0.00,probability,standard_deviation)
```

The maximum probability that David Bergman's test reports an interval of [0:0; 0:05] - 0.0473

## Problem 4.d

The confidence level of David Bergman's Test is 100%.
