---
title: "R Notebook"
author: "Anusha Karunakaran"
date: "10/03/2019"
output:
  html_document:
    df_print: paged
    toc: true
    theme: united
  html_notebook: default
  pdf_document: default
name: Anusha Karunakaran
---

# Problem 1

## Problem 1.a

<b> The problem asks for P(X > 4 crashes) </b>

```{r}
lambda_1a <- (1/2)*8
ppois(4,lambda_1a,lower.tail = FALSE)
```


## Problem 1.b

<pre>
Let X be the number of programs affected for a randomly chosen crashed computer.
Let Y be the number of additional number of programs affected (random)

X = 1 + Y, where Y is a binomial random variables, with size = 4, pi = 0.5

The PMF is:

X = 1 -> dbinom(0,4,0.5)
X = 2 -> dbinom(1,4,0.5)
X = 3 -> dbinom(2,4,0.5)
X = 4 -> dbinom(3,4,0.5)
X = 5 -> dbinom(4,4,0.5)

</pre>

```{r}
PMF_AffPgms <- c(dbinom(0,4,0.5),dbinom(1,4,0.5),dbinom(2,4,0.5),dbinom(3,4,0.5),dbinom(4,4,0.5)) 
PMF_AffPgms
```

## Problem 1.c

<pre>
Number of computers estimated to crash in an 8 hour day = 4 
X = 1 + Y, where Y is a binomial random variables, with size = 4, pi = 0.5
</pre>

```{r}
lambda_1c <- 4 
Additional_Crashes <- 4
pi <- 0.5
Program_Crashes <- lambda_1c*(1+(Additional_Crashes*pi))
Program_Crashes
```

## Problem 1.d

<pre>
Total number of program crashes 12 in a day = 12
Total number of program crashes 12 in a week = 60
</pre>

```{r}
set.seed(100)
Weekly_Crashes<- rnorm(60, mean = 30, sd = 10)
Weekly_Crashes_Minutes <- sum(Weekly_Crashes)

Hour_Rate   <- 150
Minute_Rate <- 150/60
Expected_Money  <- Weekly_Crashes_Minutes * Minute_Rate
Expected_Money
```
## Problem 1.e

<b>
Let Spend_Distribution represent the money values for each of our crashes. 
</b>

```{r}
x <- Weekly_Crashes*Minute_Rate
Quart_25 <- quantile(x, 0.25)
Quart_25
```

# Problem 2

## Problem 2.a

<pre>
 μ = 3 minutes
 
The problem asks for λ
 λ = 1/μ
   = 1/3
  
</pre>

## Problem 2.b

<b> The problem asks for P(S > 5 minutes ) = 1 - P(S <= 4 minutes) </b>

```{r}
lambda_2b <- 1/3
1- pexp(5,lambda_2b)
```

## Problem 2.c

<b> The problem asks for P(T=25 messages in next one hour) </b>


```{r}
lambda_2c <- 20
dpois(25,lambda_2c,log=FALSE)
```

## Problem 2.d

<b> The problem asks for P(T=0 emails) </b>

```{r}
lambda_2d <- (1/3)*5
dpois(0,lambda_2d,log=FALSE)
```

## Problem 2.e

<b> 
The mails coming every minute is given by λ, which is 1/3. The probability of next mail arriving in more than 5 minutes is given by,
</b>

```{r}
lambda_2e <- 1/3
pexp(5,lambda_2e,lower.tail = FALSE)
```

## Problem 2.f

<b> The sub-parts b, d and e refer to the same event.They refer to the event of getting no emails in the first five minutes </b>