---
title: "R Notebook"
author: "Anusha Karunakaran"
date: "09/26/2019"
output:
  html_document:
    df_print: paged
    toc: true
    theme: united
  html_notebook: default
  pdf_document: default
name: Anusha Karunakaran
---


# Problem 1

## Problem 1.a
<pre>
Expected Number of Attendees = μ = n*pi
where,
n = sample size 
π = probability of the event of interest for any trial
(1 – π) = probability of no event of interest for any trial


n=  325
pi= 1 - 0.08 = 0.92
Expected Number of Attendees = 325 * 0.92
                             = 299
</pre>


## Problem 1.b

<b> P(299 < X <= 325) = F(325) - F(299) </b>
```{r}
pbinom(325,325,0.92) - pbinom(299,325,0.92)
```

## Problem 1.c

<b> P(300 < X <= 325) = F(325) - F(300) </b>
```{r}
pbinom(325,325,0.92) - pbinom(300,325,0.92)
```

## Problem 1.d

<b> P(269 < X <= 299 ) </b>

```{r}
pbinom(299,325,0.92) - pbinom(269,325,0.92)
```

## Problem 1.e

<b> P(X=300) </b>
```{r}
dbinom(300,325,0.92)

```


## Problem 1.f

```{r}
# To get the maximum revenue - we need 300 seats to be filled and no people to arrive
# Let's assume we sell x tickets to fill all 300 seats up 
# x . (probability of people showing up) = 300
x <- round(300/0.92)
x

```


# Problem 2

## Problem 2.a
<pre>
Let N = Number of people show up in a given work day

Let's model N as a Poisson distribution with lambda = 8x4x3 = 96
(assume 8 hour work day)
</pre>

## Problem 2.b

<pre>
P(X>100) = 1 - F(100)
         = 1 - ppois(100,lambda)
</pre>
```{r}
Lambda <- 96
1 - ppois(100,Lambda)
```

## Problem 2.c

<b> P(3 <= X < 10) = P(X < 10) - P(X<3) </b>
```{r}
New_Lambda = 2*4*3
ppois(9,24) -ppois(2,24)
```

## Problem 2.d

<pre>
P(X > 6) = 1 - F(6)
         = 1 - ppois(6,Lambda) 
         
New_Lambda = 1*3 + 1*2 = 5
</pre>

```{r}
New_Lambda = 1*3 + 1*2
1- ppois(6,New_Lambda)
```



# Problem 3


## Problem 3.a

```{r}
c=function(n,x){
 comb = factorial(n)/(factorial(n-x)*factorial(x))
  return (comb)
}
my_dbinom = function(x,n,pi){
     return(c(n,x)*(pi^x)*((1-pi)^(n-x)))
  }
my_dbinom(2,3,0.2)
```

## Problem 3.b

```{r}
mean_binom = function(n,pi=0.5){
     meanA = n*pi
     return(meanA)
  }
mean_binom(2,0.2)
```



## Problem 3.c

```{r}
var_binom = function(n,pi=0.5){
     varA = n*pi*(1-pi)
     return(varA)
  }
var_binom(10,0.2)
```



 


