---
title: "Homework 4"
author: "Ravi Shiripurapu and Sagarika Talla"
date: "26 September 2019"

output:
  html_document:
    df_print: paged
    toc: true
    theme: united
  html_notebook: default
---


# Problem 1
Given:

The maximum number of VIP attendees that can be accommodated   = 300
The probability that a attendee doesn't show up =  0.08
Therefore, the probability that a attendee shows up p = 0.92

It is also given that the VIP booth is overbooked with n = 325

Let X be a random variable of the number of attendees who make a reservation and show up
X can be modeled using a binomial distribution with n =325 and p = 0.92

```{r}
capacity <- 300
p<-0.92
n<-325
```

## Problem 1a

Expected number of attendees that show up

```{r}
e <- n*p
e
```

In other way 

From the basic defintion that expectaed value of a discrete random variable is summation of product of random variable values and their corresponding probability
=0*P(X=0) + 1*P(X=1) +2*P(X=2)+ ...... + 325*P(X=325)

```{r}
a <- seq(0,325)
e <- sum(
        a*dbinom(a, size = 325, prob = 0.92 )
        )
e
```


## Problem 1b

probability that all seats are occupied

This happens when number of attendees shows is 300 or more
P(X>=300) = 1 - P(X<300)
          = 1 - P(X<= 299)

```{r}
1 - pbinom(299, size = 325, prob = 0.92)
```


## Problem 1c

Probability that more people show up than there is space for

This happens when the number of attendees is more than 300
P(X>300) = 1 - P(X<= 300)


```{r}
1 - pbinom(300, 325, 0.92)
```

## Problem 1d

Given that at least one of the seats is vacant, what is the probability that attendees for at
least 90% of the VIP capacity showed up?


When at least 90% of the VIP capacity showed up X takes values 0.9*300 to 300 
        ==> 270 to 300
        
A = P(270<= X <= 300)

When at least one of the seats is vacant, X takes any value from 0 to 299.
B = P(X<=299)

A n B = P(270<= X <= 299)       

Required probability is P(A/B) = P(A n B)/P(B)
                               = P(270<= X <= 299)/P(X<=299)
                               = [P(X <= 299) - P(X<= 269)]/P(X<=299)
       

```{r}
(pbinom(299,325,0.92)-pbinom(269,325,0.92))/pbinom(299,325,0.92)
```

## Problem 1e

Suppose that all of the seats are occupied. What is the probability that exactly 300 people
arrived?

A = Probability that exactly 300 people arrived; X takes value 300
  = P(X = 300)

B = All seats are occupied ; X takes values from 300 to 325
  = P(X>= 300)
  = 1 - P(X<= 299)

Required probability is P(A/B) = P(A n B)/P(B)
                               = P(X = 300)/(1 - P(X<= 299))

```{r}
dbinom(300, 325, 0.92)/(1-pbinom(299,325,0.92))
```

##Problem 1.f 

Suppose that VIP tickets sell for $250 and Eventbrite has to pay every person that shows up
and doesn't have a seat $300 on top of refunding the $250. How many VIP tickets should
Eventbrite offer to maximize revenue?

Before we answer the question let's consider the sub problem
What is the expected number of people that Eventbrite should consider refunding when 325 tickets are booked.

Tickets	| No of visitors	|	Probability
booked  | to be refunded  |

0		      0		          dbinom(0,325,0.92)
1	        0	          	dbinom(1,325,0.92)
2		      0	          	dbinom(2,325,0.92)
..	    	0	          	...
..	    	0	          	...
298	    	0	          	dbinom(298,325,0.92)
299	    	0	          	dbinom(299,325,0.92)
300	    	0	          	dbinom(300,325,0.92)
301	    	1	          	dbinom(301,325,0.92)
302	    	2	          	dbinom(302,325,0.92)
303	    	3	          	dbinom(303,325,0.92)
..				              ..
..		    		          ..
324	    	24          	dbinom(324,325,0.92)
325	    	25         		dbinom(325,325,0.92)

The above is nothing but the probability mass function of number of attendees to be refunded. 
Obsrve that the probability has an effect only when tickets booked is more than 300 which makes sense as up to 300 tickets, number of attendees to be refunded is 0  

So the expected number of attendees to be refunded 

```{r}
a <- seq(301,325)
e <- sum((a-300)*dbinom(a,325,0.92))
e
```

Expected amount to be refunded when 325 tickets are booked is e*(550)
```{r}
e*550
```
Expected revenue generated 

```{r}
325*250 - e*550
```

Let's follow this approach and calcuate the revenue When Eventbrite overbooks tickets from 301 to 350 and let's look at the trend

```{r}
Revenue <- vector(mode = "numeric", length = 50)

for (i in 301:350)
{
  j <- i-300
  g <- seq(301,i)
  Revenue[j] <- i * 250 - sum((g-300) * dbinom(g,size = i, prob = 0.92) ) * 550
  print(paste("Revenue for ",i, "tickets $",round(Revenue[j],3)))
}
print(paste("Eventbrite should sell", 300 + which(Revenue == max(Revenue)), "tickets in order to maximize the Revenue. And the maximum Revenue is $", round(max(Revenue),3)) ) 
```


#Problem 2
## Problem 2a

```{r}
lambda = 8*4*3
lambda
```

## Problem 2b

```{r}
1-ppois(100,lambda)
```

## Problem 2c

Greater than or equal to 3 but less than 10 Customer
 Time Frame: 2Hours
 
 P(2<X<=9) = F(9) - F(2)
 


```{r}
lambda2 = 2*4*3
ppois(9,lambda2) - ppois(2,lambda2)
```

## Problem 2d


To calculate P(X>=7) where Lambda is combined for two branches by adding lambdas for both the branches
```{r}

lambda3 = (1*3) + (1*2)
lambda3 = 5
1-ppois(6,lambda3)

#or

x <- replicate(10000, rpois(1,3)+rpois(1,2))
mean(x>=7)

```

#Problem 3


## Problem 3a
```{r problem3a, echo=TRUE}
my_dbinom <- function(x,n,pi){
  num <- (factorial(n)*((pi)^x)*((1-pi)^(n-x)))
  den <- (factorial(x)*factorial(n-x))
  return(num/den)
}
#or

my_dbinom = function(x,n,pi){
  return(choose(n,x)*(pi^x)*(1-pi)^(n-x))
}

dbinom(120,140,0.2)
my_dbinom(120,140,0.2)
```

## Problem 3b

```{r problem3b, echo=TRUE}
expect <- function(n,pi=0.5) {
  
  expectation = n*pi
  return(expectation)
}

```


## Problem 3c

```{r problem3c, echo=TRUE}
variance <- function(n,pi=0.5){
  
  var = (n*pi)*(1-pi)
  return(var)
}

```


