---
title: "HW2 Q1"
author: "Sagarika Talla and Ravi Shiripurapu"
date: "11 September 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Problem a
a.How many variables are in this data frame? What does each variable represent? Don't forget to include units.


```{r}
library(ISwR)
dim(women)
#There are 2 variables
#This data set gives the average heights and weights for American women aged 30-39 namely [,1]	height	 numeric	 Height (in), [,2]	weight	 numeric	 Weight (lbs)

```
#Problem b
b. Calculate the body mass index (Weight in lbs*703/height in inches2
) for every observation and create a variable BMI which records the output.

```{r}
BMI = women$weight*703/ women$height^2
```
#Problem c
c. You can add a variable x that you want to name name to a dataframe df by writing
df[name] = x.
Add the BMI to women with an appropriate column name.

```{r}
women["BMI"] =BMI
```
d. Calculate the arithmetic mean, standard deviation, skewness, and kurtosis of the BMIs without using any package or functions, except for sum() and length(), togehter with standard
mathematical operators.
```{r}

mean_bmi<-sum(BMI)/length(BMI)
mean_bmi
summary(BMI)

```

Calculating the standard deviation of the variable BodyMassIndex
```{r}
deviation_bmi<-sqrt(sum((BMI-mean_bmi)^2)/(length(BMI)-1))
deviation_bmi
sd(BMI)
```


Calculating the skewness of the variable BodyMassIndex

```{r}

skew_bmi<-((sum((BMI- mean_bmi)^3)/(length(BMI)))/
   (sum((BMI- mean_bmi)^2)/(length(BMI)-1))^(3/2))
skew_bmi
#### One can also use a package
library(e1071)
skewness(BMI)
```

Calculating the kurtosis of the variable BodyMassIndex

```{r}
kurtosis_bmi<- (1/(length(BMI))*sum( (BMI- mean_bmi)^4 ))/
 ((1/(length(BMI))*sum((BMI- mean_bmi)^2 ))^(2))

 
kurtosis_bmi


```

## Problem 1e
Yes, the distribution of BMIs is skewed. The skewness of the data is 0.69 which is greater than zero hence it is right-skewed and the median of the data is lesser than the mean.

## Problem 1f
The distribution of BMIs is platykurtic as the kurtosis is less than 3 (negative excess).A kurtosis less than 3 (negative excess) indicates that the distribution has fewer outliers, so that its tail would be flatter.

# Problem 2
## Problem 2.a
```{r}
getwd()
dataset <- read.table("filtered_qb.csv",sep=",",header=TRUE)
str(dataset)
```

## Problem 2.b
There is a slight difference in the mean for 'projections' and 'actuals' and a considerable difference in the Standard deviations for the 2 variables. 
The skewness is greater than zero for both projections and actuals variables hence both of these are right skewed with median less than the mean. 
```{r}
projections<-dataset$projections
actuals<-dataset$actuals
#arithmetic mean
mean(projections)
mean(actuals)
#standard deviation
sd(projections)
sd(actuals)
#skewness
skewness(projections)
skewness(actuals)
```

## Problem 2.c
```{r}
our.five.sum = fivenum(actuals)
our.five.sum

med = our.five.sum[3]
med
 
```
## Problem 2.d
```{r}


#boxplot for projection variable
boxplot(projections)
#boxplot for actuals variable
boxplot(actuals)
```

```{r}
#Scatterplot showing the relationship between projections and actuals variables
plot(projections,actuals)

#The projections shown in the plot are scattered or spread across without any specific pattern. Since there is no pattern observed these projections might not be very accurate for analysis but can be considered slightly accurate.
```

```{r}
 
hist(projections)
hist(actuals)
```

```{r}
#Breaks in actuals histogram
hist(actuals,breaks=10)
hist(actuals,breaks=30)

#It is observed that  more number of breaks will have more breakpoints on the histogram.

```

# Problem 3

```{r}
library(ISwR)
attach(cars)
```

## Problem 3a

```{r}
nrow(cars)
```

```{r}
copy_cars <- data.frame(cars) 
```


## Problem 3c

```{r}
copy_cars$time <- round(copy_cars$dist/copy_cars$speed,2)
```


## Problem 3d

```{r}
head(copy_cars, 14)
```

## Problem 3e

```{r}
median(copy_cars$time)
```

## Problem 3f

```{r}
fivenum(copy_cars$time)
time_q1 <- fivenum(copy_cars$time)[2]
time_q1
time_q3 <- fivenum(copy_cars$time)[4]
time_q3
```


