---
title: "R Notebook"
author: "Anusha Karunakaran"
date: "10/17/2019"
output:
  html_document:
    df_print: paged
    toc: true
    theme: united
  html_notebook: default
  pdf_document: default
name: Anusha Karunakaran
---


# Problem a
4. A risk-averse person would always prefer a greater, non-guaranteed reward to a lesser,
but guaranteed reward.

# Problem b
2. Small-cap stocks

# Problem c
3. Treasury bonds have earned a higher return than corporate bonds.

# Problem d
3. The one with a greater variance of returns.

# Problem e
Assets B and C is not dominated by any other assets in terms of return.

# Problem f

Given:
The covariance between their returns = 0.033
The Annual Return Volatility of Stock 1 = 31%
The Annual Return Volatility of Stock 2 = 34%

```{r}
Covariance <- 0.033
STD_1 <- 0.31
STD_2 <- 0.34

Correlation_Coefficient <- Covariance/(STD_1*STD_2)
round(Correlation_Coefficient,3)
```

# Problem g
Given :
Annual Stock Returns = 10%,3%,12%
Annual Market Returns = 5%,12%,8%
Time Period = 3 years


```{r}
Stock_Returns <- c(0.1,0.03,0.12)
Market_Returns <- c(0.05,0.12,0.08)
Time_Period <- 3
Correlation <-  round(cor(Stock_Returns,Market_Returns),3)
Correlation
```



# Problem h
Corelation between a stock’s returns and market returns P is 0.89.
Standard deviation of returns for the stock sdS
standard deviation of returns for the market index sdM

{r}

```{r}
Correlation_SM <- 0.89
SD1 <- 0.21
SD2 <- 0.18
Covariance_h <- Correlation_SM*SD1*SD2
Beta <- round((Covariance_h) / (SD2* SD2),2)
Beta
```



# Problem i 
```{r}
Stock_Returns_i  <- c(0.02,0.02,0.14,0.08)
Market_Returns_i <- c(0.02,0.08,0.09,0.02)
Correlation_i <- cor(Stock_Returns_i,Market_Returns_i)
Stock_Beta <- round((Correlation_i) * (sd(Stock_Returns_i)/sd(Market_Returns_i)),3)
Stock_Beta
```


# Problem j
Excel : CORREL(B2:B62,D2:D62)

```{r}
round(0.776514,3)
```


# Problem k
```{r}
Covariance_k <- 10620.17149
STD_Apple <- 21.40299548
STD_SP <- 639.0099688
Beta_Apple <- round(Covariance_k/(STD_Apple*STD_Apple),2)
Beta_Apple
```




# Problem l
2. If a stock’s returns are perfectly correlated with market returns, the beta of the stock
must be one.


# Problem m
2. With two uncorrelated assets, the standard deviation of the portfolio equals x1σR1 +
x2σR2.

# Problem n
```{r}
Weight_1 <- 20000/(20000+38000)
Weight_2= 38000/(20000+38000)
STDDEV_1 <- 0.40
STDDEV_2 <- 0.38
Correlation_n <- 0.1
Standard_Deviation_N <- round(sqrt(( (Weight_1^2) * (STDDEV_1^2) ) +( (Weight_2^2) * (STDDEV_2^2) ) + (2*Weight_1*Weight_2*Correlation_n*STDDEV_1*STDDEV_2)),2)
Standard_Deviation_N
```

