---
title: "R Notebook"
author: "Anusha Karunakaran"
date: "11/07/2019"
output:
  html_document:
    df_print: paged
    toc: true
    theme: united
  html_notebook: default
  pdf_document: default
name: Anusha Karunakaran
---


# Problem 1

## Problem 1.a
Since the population is normally distributed and we do not know the standard deviation of the  population we will use the Student T Distribution

```{r}
waiting_time_sample <- c(13.2,19,2,3,7.4,32.1,8,1,3.4,7.4,8.9,30.2,17.2)
length_wt <- length(waiting_time_sample)

```

```{r}
Standard_Error = sd(waiting_time_sample)/sqrt(length_wt)
Standard_Error
```
```{r}
#1-alpha = 0.85
alpha = 1 - 0.85
alpha
alphaby2 = alpha/2
alphaby2
ci = 1-alphaby2
ci
UB_wt = mean(waiting_time_sample)+ Standard_Error*qt(0.925,df=12)
UB_wt
LB_wt = mean(waiting_time_sample)- Standard_Error*qt(0.925,df=12)
LB_wt
```

## Problem 1.b
Since the population standard deviation is given, we can find the confidence interval like below:

```{r}
mean_wt = mean(waiting_time_sample)
mean_wt
Critical_value = qnorm(alphaby2)
Critical_value
Critical_Value_Wt = 1.44
Critical_Value_Wt
```


```{r}
UpperBound=qnorm(0.925,mean=mean_wt,sd=10/sqrt(13))
UpperBound
LowerBound=qnorm(0.075,mean=mean_wt,sd=10/sqrt(13))
LowerBound
```


## Problem 1.c
When we don't know if the population is normally distributed, we can use the method of bootstrapping:

```{r}
set.seed(100)
sampling_dist <- replicate(1000,mean(sample(waiting_time_sample,size=length_wt,replace=TRUE)))
LB <- quantile(sampling_dist,0.075)
LB
UB <- quantile(sampling_dist,0.925)
UB
```

## Problem 1.d
<pre>
Suppose you know that the population waiting time is exponentially distributed. Build a 85%
confidence interval for the mean waiting time.

Mean = 11.75
N = 13 
SD = 10.22
</pre>
For exponential distribution 

```{r}
A = 1.9
pexp(A) - pexp(-A)
```

Therefore , 
```{r}
pnorm(1.9)
qnorm(0.971)
```

for exponential distribution 

```{r}
xbar_spl = mean(waiting_time_sample)
SD_spl = sd(waiting_time_sample)
sampling_sd = SD_spl/sqrt(13)
upper_exp = xbar_spl + qexp(0.971) * sampling_sd
upper_exp
lower_exp = xbar_spl + qexp(0.029) * sampling_sd
lower_exp

```

The confidence interval for the exponential distribution is [21.79, 11.83]



# Problem 2

## Problem 2.a
<pre>
Power Drills that work: 253 
Power Drills that doesn't work: 7
p = 7/260 
</pre>

For 95% confidence interval,
```{r}
A = 1.965 
pnorm(A) - pnorm(-A)

```

```{r}
pnorm(1.965)
qnorm(0.975)
```


```{r}
n <- 260
p <- 7/260 
sep_power = sqrt(7/260*(1- 7/260)/260)
sep_power
```

```{r}
upperb_power = qnorm(0.975 , mean = 7/260, sd = sep_power)
upperb_power
lowerb_power = qnorm(0.025, mean = 7/260 , sd = sep_power)
lowerb_power

```

95% Confidence interval for the proportion of power drills that don't work is [0.0465 , 0.007]


## Problem 2.b
<pre>
Power Drills that work: 200
Power Drills that doesn't work: 60
p = 60/260 
</pre>

For 95% confidence interval,
```{r}
A = 1.965 
pnorm(A) - pnorm(-A)

```

```{r}
pnorm(1.965)
qnorm(0.975)
```


```{r}
n <- 26060
p <- 60/260 
sep_power = sqrt(60/260*(1- 60/260)/260)
sep_power
```

```{r}
upperb_power = qnorm(0.975 , mean = 60/260, sd = sep_power)
upperb_power
lowerb_power = qnorm(0.025, mean = 60/260 , sd = sep_power)
lowerb_power

```

95% Confidence interval for the proportion of power drills that don't work is [0.281,0.179]


# Problem 3

## Problem 3.a
Null Hypothesis: H0: The company has insufficient shelving units to satisfy daily demand

## Problem 3.b
Alternate Hypothesis: H1: The company has sufficient shelving units to satisfy daily demand

## Problem 3.c
μ0 = 162

## Problem 3.d
Mean

## Problem 3.e
Mean number of tanks sold which is 150.8

## Problem 3.f
No. Since the sample size > 30, we can substitute the sample standard deviation for the population standard deviation.

## Problem 3.g
```{r}
Mu0 = 162
xBar <- 150.8
s <- 50.3
SE <- s/sqrt(32)
df <- 32-1
```

#### using Z-test
```{r}
UB_Z <- Mu0 - SE*qnorm(0.9)
UB_Z

print(paste("For Z- test, xBar that is lesser than ",round(UB_Z,2), " will lead to rejection of the null hypothesis"))
```

#### Using t-test
```{r}
UB_t <- Mu0 - SE*qt(0.9, df)
UB_t
print(paste("For t-test, xBar that is lesser than ",round(UB_t,2), " will lead to rejection of the null hypothesis"))
```


## Problem 3.h

```{r}
Mu0 = 162
xBar <- 150.8
s <- 50.3
SE <- s/sqrt(32)
df <- 32-1
```

#### using Z-test
```{r}
UB_Z <- Mu0 - SE*qnorm(0.95)
UB_Z
print(paste("For Z- test, xBar that is lesser than ",round(UB_Z,2), " will lead to rejection of the null hypothesis"))
```


#### Using t-test
```{r}
UB_t <- Mu0 - SE*qt(0.95, df)
UB_t
print(paste("For t-test, xBar that is lesser than ",round(UB_t,2), " will lead to rejection of the null hypothesis"))
```



## Problem 3.i

```{r}
Mu0 = 162
xBar <- 150.8
s <- 50.3
SE <- s/sqrt(32)
df <- 32-1
```

#### using Z-test
```{r}
UB_Z <- Mu0 - SE*qnorm(0.99)
UB_Z
print(paste("For Z- test, xBar that is lesser than ",round(UB_Z,2), " will lead to rejection of the null hypothesis"))

```


#### Using t-test
```{r}
UB_t <- Mu0 - SE*qt(0.99, df)
UB_t
print(paste("For t-test, xBar that is lesser than ",round(UB_t,2), " will lead to rejection of the null hypothesis"))
```



## Problem 3.j
```{r}
Mu0 = 162
xBar <- 150.8
s <- 50.3
SE <- s/sqrt(32)
df <- 32-1
TS <- (xBar - Mu0)/SE
```

#### using Z-test
```{r}
UB_Z <-  -1 * qnorm(0.90)
UB_Z
print(paste("For Z- test, TS is " ,round(TS,2), " that is lesser than ",round(UB_Z,2), " will lead to rejection of the null hypothesis"))
```


#### Using t-test
```{r}
UB_t <-  -1 * qt(0.90, df)
UB_t
print(paste("For t-test, TS is " ,round(TS,2), "that is lesser than ",round(UB_t,2), " will lead to rejection of the null hypothesis"))

```


## Problem 3.k
```{r}
Mu0 = 162
xBar <- 150.8
s <- 50.3
SE <- s/sqrt(32)
df <- 32-1
TS <- (xBar - Mu0)/SE
```

#### using Z-test
```{r}
UB_Z <-  -1 * qnorm(0.95)
UB_Z
print(paste("For Z- test,TS is " ,round(TS,2), " that is lesser than ",round(UB_Z,2), " will lead to rejection of the null hypothesis"))
```

#### Using t-test
```{r}
UB_t <-  -1 * qt(0.95, df)
UB_t
print(paste("For t-test,TS is " ,round(TS,2), "that is lesser than ",round(UB_t,2), " will lead to rejection of the null hypothesis"))
```



## Problem 3.l
```{r}
Mu0 = 162
xBar <- 150.8
s <- 50.3
SE <- s/sqrt(32)
df <- 32-1
TS <- (xBar - Mu0)/SE
```


#### using Z-test
```{r}
UB_Z <-  -1 * qnorm(0.99)
UB_Z
print(paste("For Z- test, TS is " ,round(TS,2), " that is lesser than ",round(UB_Z,2), " will lead to rejection of the null hypothesis"))
```

#### Using t-test

```{r}
UB_t <-  -1 * qt(0.99, df)
UB_t
print(paste("For t-test, TS is " ,round(TS,2), "that is lesser than ",round(UB_t,2), " will lead to rejection of the null hypothesis"))
```


## Problem 3.m
P(xBar >= 162)
P(TS >= 162)

#### Based on Xbar
```{r}
Mu0 = 162
xBar <- 150.8
s <- 50.3
SE <- s/sqrt(32)
df <- 32-1
```


#### According to t test
```{r}
pt(((xBar-Mu0)/(SE)),df)
```

#### According to z test
```{r}
pnorm(((xBar-Mu0)/(SE)))
```

#### Based on TS
```{r}
TS <- (xBar - Mu0)/SE
```

#### According to t test
```{r}
pt(TS,df)

```

#### According to z test
```{r}
pnorm(TS)
```


## Problem 3.n
P(xBar >= 162)
P(TS >= 162)

#### Based on Xbar
```{r}
Mu0 = 162
xBar <- 150.8
s <- 50.3
SE <- s/sqrt(32)
df <- 32-1
```

#### According to t test
```{r}
pt(((xBar-Mu0)/(SE)),df)
```

#### According to z test
```{r}
pnorm(((xBar-Mu0)/(SE)))
```

#### Based on TS
```{r}
TS <- (xBar - Mu0)/SE
```

#### According to t test
```{r}
pt(TS,df)
```

#### According to z test
```{r}
pnorm(TS)
```


## Problem 3.o
We observe that the p value are a representation of the probability of finding a sample result as extreme as the given sample result GIVEN THAT H0 is true. 

For 'Z' Test, In this case, the p value is observed to be 0.1039 i.e. value as extreme as 150.8 and below can be found with probability of 10.39%. So, we can only reject H0 if the confidence level is 89.60% or lower (ref. Problem 3.n). 

For 'T' Test, In this case, the p value is observed to be 0.1086 i.e. value as extreme as 150.8 and below can be found with probability of 10.86%. So, we can only reject H0 if the confidence level is 89.13% or lower (ref. Problem 3.n). 

The rejection region for 90% in 'Z' test is <= -1.28 for the transformed test statistic. (ref. Problem 3.j). Rejection region reduces as the confidence level desired increases ( ref Problem 3.k and 3.l). Hence, the given sample can't reject the H0, as also proved by the p value. 

Likewise, The rejection region for 90% in 'T' test is <= -1.30 for the transformed test statistic. (ref. Problem 3.j). Rejection region reduces as the confidence level desired increases ( ref Problem 3.k and 3.l). Hence, the given sample can't reject the H0, as also proved by the p value.



# Problem 4

## Problem 4.a
```{r}
n <- 30
SD1 <- 5700
SD2 <- 20000
Width1 <- 2*qnorm(0.95)*(SD1/sqrt(n))
Width2 <- 2*qnorm(0.95)*(SD2/sqrt(n))
Width1
Width2
```

Maximum width is with 20000 standard deviation and the value is 12012.

## Problem 4.b
```{r}
house <- vector()
house <- lapply(5700:20000, function(x){
  house <- (20000 + 2*qnorm(0.95)*(x/sqrt(30))) - 1950
  return(house)
})

length(house)
```

