---
title: "R Notebook"
author: "Anusha Karunakaran"
date: "10/10/2019"
output:
  html_document:
    df_print: paged
    toc: true
    theme: united
  html_notebook: default
  pdf_document: default
name: Anusha Karunakaran
---

# Problem 1

<pre>
The problem can be solved by Conditional Probability.

Let us assume that there are two events A and B where ,

A is an event specifying an aircraft is present
B is an event specifying the radar registers an aircraft is present 

A' is an event specifying an aircraft is not present
B' is an event specifying the radar registers an aircraft as not present

Given :
P(A) = 0.05

P(B|A) = 0.98

P(B|A') = 0.10

The probability of an aircraft not present = 1 - P(A)
                                           = 1 - 0.05
                                           = 0.95
                                          
</pre>

```{r}
A_Complement <- 0.95
B_Given_A_Complement <- 0.10
# Since A Complement and B|A' are two independent events, 
# The probability of false alarm = P(A')* P(B|A')

False_ALarm <- A_Complement * B_Given_A_Complement
False_ALarm

```

<pre>
The probability that the radar falsely registers an aircraft is not present(miss detection) is:
P(B'|A) = 1 - P(B|A)
        = 1 - 0.98
        = 0.02
</pre>
        
        
```{r}
A <- 0.05
B_Complement_Given_A <- 0.02
# Since A and B'|A are two independent events, 
# The probability of Missed Detection = P(A)* P(B'|A)
Missed_Detection <- A * B_Complement_Given_A
Missed_Detection
```

<pre>
Solution:

The probability of false alarm = 0.095
The probability of missed detection = 0.001
</pre>

# Problem 2

Store 1: (Poisson)
1 person every 30 seconds

Store 2: (Normal Distribution)
Mean = 120
S.D = 20

Store 3: (Normal Distribution)
Mean = 100
S.D = 20


## Problem 2.a
```{r}
lambda_2a <- 1 * 2 * 60
Variance  <- sqrt(lambda_2a)
Variance
```

## Problem 2.b
```{r}
Expected_Store1 <- 1 * 2 * 60
Expected_Store2 <- dnorm(1,mean=120,sd=20)
Expected_Store3 <- dnorm(1,mean=100,sd=20)
Total_Expected_Value <- Expected_Store1 + Expected_Store2 + Expected_Store3
Total_Expected_Value
```

## Problem 2.c

```{r}
Variance1 <- sqrt(1 * 2 * 60)
Expected_Store2 <- dnorm(1,mean=120,sd=20)
Expected_Store3 <- dnorm(1,mean=100,sd=20)

```


## Problem 2.d

```{r}
Store1_Prob <- dpois(1,24*2*60)
Store1_Prob
Store2_Prob <- dnorm(24,mean=120,sd=20)
Store2_Prob

# Store 2 is more
```


# Problem 3

## Problem 3.a
X = {0,1,2,3,4,....}
As the value of X increases, the cumulative probability of a success approaches 1.

## Problem 3.b

Given:
Success Probability (p) = 1/6

Find:
Expected Value

```{r}
# Expected Value
p <- 1/6
Expected_Value <- (1-p)/p
Expected_Value

# Expected Value using Simulation
mean(rgeom(n = 10000,prob = p))
```


## Problem 3.c

Given:
Success Probability (p) = 1/6

Find:
Skewness

```{r}
# Skewness
p <- 1/6
Skewness <- (2-p)/(sqrt(1-p))
Skewness

#Skewness using Simulation

```

## Problem 3.d