---
title: "Lecture 5"
author: "David Bergman"
date: "09/26/19"
output:
  html_document:
    number_sections: yes
    toc: yes
---

Let N be the number of complaints in an 8-hour day.

We will model N as a Poisson random variable.  

expected number: 24

```{r}
rpois(100,24)
```

```{r}
mean(rpois(10000,24))
```

```{r}
number_of_complains_sim <- rpois(10000,24)
```

```{r}
fewer_than_20 <- number_of_complains_sim < 20
```

```{r}
sum(fewer_than_20)/length(fewer_than_20)
```

```{r}
ppois(19,24)
```

SAMPLE

```{r}
random_draw <- sample( c(0,1,2,3)  , 
                       100, 
                       replace = TRUE,  
                       prob = c(0.6,0.2,0.1,0.1))
random_draw
mean(random_draw)
```

```{r}
random_draw <- replicate(100,rpois(1,24))
mean(random_draw)
```


Slide 35
```{r}
random_draw <- replicate( 10000 ,
                          rpois(1,24) +
                          rbinom(1,325,0.05))
# Estimated average
mean(random_draw)
# Estimated variance
var(random_draw)
sd(random_draw)
# prob of angry
angry_sim <- random_draw >= 50
angry_sim
sum(angry_sim)/length(angry_sim)
```




```{r}
dnorm(0,mean=0,sd=0.000001)
```


```{r}
5*10
```


```{r}
mean(replicate( 1000, sum(rnorm(rpois(1,100),5,1))))
```


Suppose a bus will arrive to a stop between 2 and 6 minute
from now, uniformly distributed in that range

What is f(3)
```{r}
#f(3)
dunif(3,min=2, max=6)

#f(1)
dunif(1,min=2, max=6)

#F(3)
punif(3,min=2,max=6)

#f(4)
dunif(4,min=2,max=6)
#F(4)
punif(4,min=2,max=6)

# randomly draw
runif(100,min=2,max=6)

```

Suppose the expected time between 
arrivals of trucks to a depot is 10 minutes
The weight of items in each truck is normally distributed
with mean of 1000 pounds and standard deviation 15

What is the expected number of pounds of material that has to be 
unloaded during 1 hour?

```{r}

rpois(1,6)


sum(
  rnorm( rpois(1,6) , 1000, 15 )
)

simulated_values <- replicate(1000,
                                sum(
                                  rnorm( rpois(1,6) , 1000, 15 )
                                )
                              )
mean(simulated_values)
```
 
in one hour you only have capacity to unload 8000 pounds.
what is the probability that you will be unable to unload the entire 
demand in one hour?


```{r}
too_large <- simulated_values > 8000
sum(too_large)/length(too_large)

```




# Slide 51

Let T be the number of hours between consecutive arrivals 

```{r}

lambda = 20
```


```{r}

# P( T < 6 minutes ) = P(T < .1 Hours) = P(T <= .1 Hours)
pexp(.1,lambda)
```


```{r}

# Let S be the number of minutes between consecutive arrivals 
lambda_s = 1/3

# P( S <= 6 minutes ) 
pexp(6,lambda_s)


# 



qnorm(0,mean=0,sd=1)

qnorm(0.4,mean=0,sd=1)


qnorm(0.6,mean=0,sd=1)


qunif(0.5,min=10,max=20)


qunif(0,min=10,max=20)


qunif(1,min=10,max=20)



# What is the value for which 40% of the distribution is to my left?













```















