---
title: "Homework 4 Solutions"
output: html_notebook
---
# Problem 1
Let X be the random variable of the number of students that matriculate
This can be modeled as a binomial distribution with success probability (matriculation), p = 0.15
```{r}
p<-0.15
```

## Problem 1a
The expected value of the random variable X is given by E(X) = np
```{r}
n<-1000
n*p
```

## Problem 1b
The standard deviation of the random variable X is given be sigma = sqrt(np*(1-p))
```{r}
sqrt(n*p*(1-p))
```

## Problem 1c
Let us examine what information is given. The university wants at most 160 students to matriculate. Also, since it is given that the university wants to be 99.5% sure, they want the probability of at most 160 students matriculating to be 0.995
Hence, it is given that P(X<=160) = 0.995
To find: Sample size (n) for which this happens

Let us first assume n=1000 and calculate the maximum number of students matriculating with 99.5% certainity
```{r}
qbinom(p = 0.995,size = 1000,prob = 0.15)
```
This is higher than what we need. Now, let us try n=900
```{r}
qbinom(p = 0.995,size = 900,prob = 0.15)
```
This is very close to what we need. Now, let us try n=875
```{r}
qbinom(p = 0.995,size = 875,prob = 0.15)
```
This is lesser than what we need but extremely close as well! Now, let us try n=880
```{r}
qbinom(p = 0.995,size = 880,prob = 0.15)
```
We get 160 for n=880. However, the question asks for the maximum number of students that they can offer admission to.
Hence, let us try n=881 to n=885
```{r}
qbinom(p = 0.995,size = 881,prob = 0.15)
qbinom(p = 0.995,size = 882,prob = 0.15)
qbinom(p = 0.995,size = 883,prob = 0.15)
qbinom(p = 0.995,size = 884,prob = 0.15)
qbinom(p = 0.995,size = 885,prob = 0.15)
```
We see that we get 160 until n=883 after which it crosses 160. Hence, the required sample size is n=883

# Problem 2
Given:
The maximum number of passengers the flight can have (capacity) = 70
The probability that a passenger shows up (p) =  0.93
Therefore, the probability that a passenger does not show up (1-p) = 1-0.93 = 0.07

It is also given that the flight is overbooked with n = 73

Let X be a random variable of the number of passengers who make a reservation and show up
X can be modeled using a binomial distribution with n =73 and p = 0.93
```{r}
capacity <- 70
p<-0.93
n<-73
```

## Problem 2a
The situation where more people show up than the airplane has capacity for happens when X=71 or X=72 or X=73
Hence, To find: P(X>70) = 1 - P(X<=70)
```{r}
1 - pbinom(q = capacity,size = n,prob = p)
```

## Problem 2b
90% of capacity = 0.9*70 = 63
Since we want fewer than 90% of seats to be occupied, the required probability is P(X<63) = P(x<=62)
```{r}
pbinom(0.9*capacity - 1,size = n,prob = p)
```
## Problem 2c
The expected number of passengers that show up is given by E(X) = np
```{r}
n*p
```
Although the value is not a whole number, it should not be rounded to the nearest whole number since the expected value of a random variable taking integer values need not be a whole number as it is a measure of central tendency.

## Problem 2d
If X is a random variable for the number of passengers who make a reservation and show up,
then let Y be a random variable for the amount of money paid to customers who are turned away.
Y can be defined as Y = {200*(x-70) if x>70; 0 otherwise}
For n = 73, 
the values that Y can take are {0 if x<=70; 200 if x=71; 400 if x=72; 600 if x=73} and the associated probabilities for these values of Y are {P(X<=70) if x<=70; P(X=71) if x=71; P(X=72) if x=72; P(X=73) if x=73}

Hence, the expected value of the amount of money paid to customers who are turned away (Y) is given by the sum of the product of the values of Y and their corresponding probabilities.
```{r}
Y<-c(0,200,400,600)
prob<-c(pbinom(70,n,p),dbinom(71,n,p),dbinom(72,n,p),dbinom(73,n,p))
sum(Y*prob)
```

## Problem 2e

Now to find the tickets with the maximum expected revenue, we will pass the number of expected tickets throught a loop / perform a binary search for each case , and calculate the expected value of the Discreate PMF from 1 to X where X is the number of tickets considered. 

For 71 tickets we will have 
P(1)X 150 + P(2) X 300 .... P(70)X150X70 + P(71)X 71X (150) - dbinom(71) *200

Similary

```{r}
a<-seq(71,90,1)

for(i in 1:length(a))
{
n_tix_sold<-a[i]
num_show_up <- seq(0,n_tix_sold)
pmf_num_show_up <- dbinom(num_show_up,size=n_tix_sold,prob=0.93)

profit_for_first_70_values <- 150*seq(0,70)

profit_for_next_X_values <- -50*seq(n_tix_sold-70,1) + 70*150

profit_for_all_values = c(profit_for_first_70_values,profit_for_next_X_values)

expected_profit <- sum(pmf_num_show_up*profit_for_all_values)
print(paste(a[i],expected_profit))
}
```

## Problem 2f
Given:
n = 73
p = 0.93
A - 70 seats are occupied => 70 passengers have shown up for sure => the number of people who actually showed up could be 70 or more (X = 70,71,72,73)

To find:
P(X>70|A)
```{r}
(1-pbinom(capacity,n,p))/(1-pbinom(69,n,p))
```

## Problem 2g
Let X be a random variable of the number of economy passengers who make a reservation and show up
Let Y be a random variable of the number of business passengers who make a reservation and show up

Given:
The probability of business class passengers showing up (p_bus) = 0.75
The probability of economy class passengers showing up (p_econ) = 0.93

There are 4 business class seats and 66 economy class seats and that the airline has oversold 2 business class seats and 2 economy seats. 

Hence, n_bus = 6
n_econ = 68
n_total = 68 + 6 = 74

Now, there are 3 cases where n_total > 72
They are as follows:

Case 1: 68 economy and 6 business passengers turn up => P(X=68)*P(Y=6)
Case 2: 68 economy and 5 business class passengers turn up => P(X=68)*P(Y=5)
Case 3: 67 economy and 6 business class passengers turn up => P(X=67)*P(Y=6)

To find:
P(X > 72) = P(Case 1) + P(Case 2) + P(Case 3) 
```{r}
n_bus <- 6
n_econ <- 68
p_bus <- 0.75
p_econ <- 0.93

P_case1 <- dbinom(68,n_econ,p_econ)*dbinom(6,n_bus,p_bus)
P_case2 <- dbinom(68,n_econ,p_econ)*dbinom(5,n_bus,p_bus)
P_case3 <- dbinom(67,n_econ,p_econ)*dbinom(6,n_bus,p_bus)

P_case1 + P_case2 + P_case3
```


# Problem 3
## Problem 3a
X = {0,1,2,3,4,....}
As the value of X increases, the cumulative probability of a success approaches 1.

## Problem 3b
X = 0 means that we get a 3 in the first roll of the die. The probability of that happening is 1/6 which is the success probability itself.

## Problem 3c
X = 1 means that we do not get a 3 in the first roll AND we get a 3 in the second roll. Hence, we require the joint probability of these two events. 
Since the probability that we do not roll a 3 is 5/6, 
P(X=1) = (5/6)*(1/6) = 5/36

## Problem 3d
X = 2 means that we do not get a 3 in the first two rolls AND we get a 3 in the third roll. Hence, we require the joint probability of these three events. 

P(X=2) = (5/6)*(5/6)*(1/6) = 25/216

## Problem 3e
```{r}
# P(x=0)
dgeom(x = 0,prob = (1/6))
# P(x=1)
dgeom(x = 1,prob = (1/6))
# P(x=2)
dgeom(x = 2,prob = (1/6))
```

## Problem 3f
If the 11th customer buys a computer, it means 10 customers before him did not buy a computer.
```{r}
dgeom(x = 10,prob = 0.03)
```

## Problem 3g
```{r}
?pgeom
#P(X>=30)
1 - pgeom(q = 29,prob = 0.03)

1 - pbinom(29,30,0.97)
dbinom(30,30,0.97)
```
This represents the nature of random variables that can be represented as two different distributions for a particular phenomenon. This can be written as 
X - a geom random variable for the number of people who enter the store and not buy 
Y - a binom random variable for the number of people who dont buy a laptop 
Both X and Y can explain the probability that the first 30 customers will not buy

## Problem 3h
```{r}
p<-0.03
expected_customers <- (1-p)/p
expected_customers
var_customers <- (1-p)/(p^2)
var_customers
```

## Problem 3i
```{r}
mean(rgeom(n = 10000,prob = 0.03))
```
Yes, the arithmetic mean of the generated distribution roughly coincides with the expected value in 3h. This is because the generated distribution is a geometric distribution and since the number of values is large enough, the sample mean is very close to the population mean. 
