---
title: "Exam1Solution"
output: html_notebook
---

# Problem 1

Let the students be designated by 1, 2, 3.

Let A be the event that student 1 enroll
Let B be the event that student 2 enroll
Let C be the event that student 3 enroll

```{r}
pA = 1.0
pB = 0.3
pC = 0.6
```


## Problem 1a

Let X be the number of students that enroll

X can take values 1, 2, 3

```{r}
xValues = c(1,2,3)
```


X = 1 if and only if student 2 and 3 do not enroll
X = 3 if and only if student 2 and 3 do enroll
X = 2 otherwise

```{r}
p1 = (1-pB)*(1-pC)
p3 =pB*pC
p2 = 1 - p1 - p3
xProb = c(p1,p2,p3)
print(xProb)
```


## Problem 1b


```{r}
xProb[2] + xProb[3]
```

## Problem 1c

```{r}
sum(xProb * xValues)
```

## Problem 1d

There are 4 possibilities, and so we find the average GPA for each possibility and the probability


```{r}
gpas = c(3.3,3.9,3.8)
```


Case 1: Only student 1


```{r}
prob_1 = pA * (1-pB) * (1-pC)
avg_gpa_1 = gpas[1]/1
```

Case 2: Student 1 and student 2 only 

```{r}
prob_2 = pA * pB * (1-pC)
avg_gpa_2 = (gpas[1]+gpas[2])/2
```

Case 3: Student 1 and student 3 only 

```{r}
prob_3 = pA * (1-pB) * pC
avg_gpa_3 = (gpas[1]+gpas[3])/2
```

Case 4: Student 1, student 2, and student 3

```{r}
prob_4 = pA * pB * pC
avg_gpa_4 = (gpas[1]+gpas[2] + gpas[3])/3
```

Expected values is sum of probs times values

```{r}
prob_1 * avg_gpa_1 + prob_2 * avg_gpa_2 + prob_3 * avg_gpa_3 + prob_4 * avg_gpa_4
```

## Problem 1e

Change the inputs:

```{r}
pA = 1.0
pB = 0.3
pC = 0.8
```


We don't know the gpa, but let's first test with what we had before

```{r}
possibleGPA = 3.8
gpas = c(3.3,3.9,possibleGPA)
```

Lets calculate expected GPA


```{r}
prob_1 = pA * (1-pB) * (1-pC)
avg_gpa_1 = gpas[1]/1
prob_2 = pA * pB * (1-pC)
avg_gpa_2 = (gpas[1]+gpas[2])/2
prob_3 = pA * (1-pB) * pC
avg_gpa_3 = (gpas[1]+gpas[3])/2
prob_4 = pA * pB * pC
avg_gpa_4 = (gpas[1]+gpas[2] + gpas[3])/3
prob_1 * avg_gpa_1 + prob_2 * avg_gpa_2 + prob_3 * avg_gpa_3 + prob_4 * avg_gpa_4
```

Before it was 3.507, so this is still OK!  But, we want the minimum, so we guess and check (you can also solve this analytically)

```{r}
possibleGPA = 3.6917
gpas = c(3.3,3.9,possibleGPA)
prob_1 = pA * (1-pB) * (1-pC)
avg_gpa_1 = gpas[1]/1
prob_2 = pA * pB * (1-pC)
avg_gpa_2 = (gpas[1]+gpas[2])/2
prob_3 = pA * (1-pB) * pC
avg_gpa_3 = (gpas[1]+gpas[3])/2
prob_4 = pA * pB * pC
avg_gpa_4 = (gpas[1]+gpas[2] + gpas[3])/3
prob_1 * avg_gpa_1 + prob_2 * avg_gpa_2 + prob_3 * avg_gpa_3 + prob_4 * avg_gpa_4
```


Approximately 3.6917


# Problem 2

Let A be the event that a randomly chosen motherboard is provided by company X
Let B be the event that a randomly chosen motherboard is provided by company Y
Let C be the event that a randomly chosen motherboard is provided by company Z

```{r}
pA = 0.75
pB = 0.2
pC = 0.05
```

Let D be the event that a randomly chosen motherboard is defective

```{r}
pD_givenA = 0.04
pD_givenB = 0.03
pD_givenC = 0.024
```

## Problem 2a

This is asking for P(D)

```{r}
pD = pD_givenA * pA + pD_givenB * pB + pD_givenC * pC 
pD
```

## Problem 2b

Asking for P(C|D) = p(C and D)/p(D) = p(D|C)*P(C)/p(D)

```{r}
pC_givenD = pD_givenC*pC / pD
pC_givenD
```

# Problem 3

Number of trouts caught each day is a Poisson distribution with lambda=18
Number of pampanos caught each day is a Binomial distribution with n=12 and p=0.7

Cost of scaling trout is normally distributed with mean = 1 and sd = 0.1
Cost of scaling pampano is uniformly distributed with min = 1 and max = 1.25

Revenue from selling a trout is uniformly distributed with min = 15 and max = 22
Revenue from selling a trout is uniformly distributed with min = 22 and max = 27

```{r}
lambda <- 18
n <- 12
p <- 0.7
P_T_throw<-0.1
P_P_throw<-0.2

T_scale_cost_mean <- 1
T_scale_cost_sd <- 0.1
P_scale_cost_min <- 1
P_scale_cost_max <- 1.25

P_T_purchase <- 0.9
P_P_purchase <- 0.85

T_rev_min <- 15
T_rev_max <- 22

P_rev_min <- 22
P_rev_max <- 27
```

## Problem 3a
Expected number of fish caught = E_trout (Poisson) + E_pampano (Binomial)
```{r}
lambda + n*p
```

## Problem 3b
Number of trouts that are not thrown away can be modeled using a binomial distribution 
  with n = no. of trouts caught (from Poisson)
       p = 1 - Prob of throwing away a trout fish

Number of pampanos that are not thrown away can be modeled using a binomial distribution 
  with n = no. of pampanos caught (from Binomial)
       p = 1 - Prob of throwing away a pampano fish

Number of trouts that are sold can be modeled using a binomial distribution 
  with n = no. of trouts remaining after satisfying weight requirements
       p = Prob of a trout fish being purchased

Number of pampanos that are sold can be modeled using a binomial distribution 
  with n = no. of pampanos remaining after satisfying weight requirements
       p = Prob of a pampano fish being purchased

Since some fish are thrown back into the ocean, only those that are not thrown away are scaled.

```{r}
mean(replicate(10000,
          rbinom(1,rbinom(1,rpois(1,lambda),1-P_T_throw),P_T_purchase) + 
          rbinom(1,rbinom(1,rbinom(1,n,p),1-P_P_throw),P_P_purchase)
          )
    )
```

## Problem 3c
The number of fish that remain after satisfying weight requirements becomes the first argument for rnorm as the cost of scaling each fish varies uniformly.

```{r}
cost<-replicate(10000,
          sum(rnorm(rbinom(1,rpois(1,lambda),1-P_T_throw),T_scale_cost_mean,T_scale_cost_sd)) + sum(runif(rbinom(1,rbinom(1,n,p),1-P_P_throw),P_scale_cost_min,P_scale_cost_max))
 )

mean(cost)
```

## Problem 3d
```{r}
sum(cost>23)/length(cost)
```

## Problem 3e

To simulate for the daily operating revenue, we need to simulate the operating revenue for one random day and iterate the process to generate a distribution.

```{r}
op_rev<-vector(mode = "numeric")

for (i in 1:10000){
 T_before_purchase<-rbinom(1,rpois(1,lambda),1-P_T_throw)
 T_sold<-rbinom(1,T_before_purchase,P_T_purchase)

 P_before_purchase<-rbinom(1,rbinom(1,n,p),1-P_P_throw)
 P_sold<-rbinom(1,P_before_purchase,P_P_purchase) 
 
 op_rev_iter <-
 (
  sum(runif(T_sold,T_rev_min,T_rev_max))
  +
  sum(runif(P_sold,P_rev_min,P_rev_max))
  -
  sum(rnorm(T_before_purchase,T_scale_cost_mean,T_scale_cost_sd))
  -
  sum(runif(P_before_purchase,P_scale_cost_min,P_scale_cost_max))
 )
 
 op_rev <- c(op_rev,op_rev_iter)
}


var(op_rev)

```




# Problem 4


Let D be the event that a randomly chosen person has the disease

Let T be the event that a randomly chosen person tests positive for the disease

We are given:

P(T|D) = 0.95
P(T|notD) = 0.01
P(D) = 0.005

## Problem 4a

The problem asks for P(T)

```{r}
pT_givenD = 0.05
pT_givenNotD = 0.01
pD = 0.005
pNotD = 1-pD
pT = pT_givenD*pD + pT_givenNotD*pNotD
pT
```

## Problem 4b

Asking for P(D|T) = P(D and T)/P(T) = P(T|D)*P(D) / P(T)

```{r}
pD_givenT = pT_givenD*pD / pT
pD_givenT
```


## Problem 4c

Asking for P(notD|notT) = P(notD and notT) / P(notT) 
                        = (P(notT|notD)*p(notD)  )/ (1-p(notT))
                        = ((1-P(T|notD))*p(notD)  )/ (1-p(notT))
                        
```{r}
pNotD_givenNotT = ( (1-pT_givenNotD) * pNotD ) / (1-pT)
pNotD_givenNotT
```


# Problem 5

## Problem 5a

False.  Take a uniform between 0 and 0.1

## Problem 5b

True. The pmf gives probabilities.

## Problem 5c

False.  They are collectively exhaustive (one must happen) and mutually exclusive (they cannot both happen)

## Problem 5d

Question discarded

## Problem 5e

True. If P(B) = 1, then P(A | B) = P(A)

# Problem 6


## Problem 6.a

```{r}
n = 10
pi = 0.4
```

```{r}
mean_Y = n*pi
sd_y = n*pi*(1-pi)
cv_y = sd_y / mean_Y * 100
```

## Problem 6.b

```{r}
stocks_df <- read.csv("Data/stocks.csv")
```


## Problem 6.c

```{r}
n = length(stocks_df$A)
print(n)
```

```{r}
cv_est_A <- (1+1/(4*n))*sd(stocks_df$A)/mean(stocks_df$A)
cv_est_B <- (1+1/(4*n))*sd(stocks_df$B)/mean(stocks_df$B)
```

## problem 6.d

```{r}
library(raster)
rand_vals <- rnorm(10,10,1)
cv(rand_vals)
```

```{r}
est_cv <- (1+1/40)*sd(rand_vals)/mean(rand_vals)*100
print(est_cv)
```


No! The values are a bit differnet
